### 2016-12-01 doc/final/manuscript.tex
Makefile Commit

% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate-05-2015}

\begin{document}

% Copyright
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{10.475/123_4}

% ISBN
\isbn{123-4567-24-567/08/06}

%Conference
%\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

%\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{ISSTA}{'17 Santa Barbara, CA USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Multi-Objective Search in Automated Patch Generation
\titlenote{(Produces the permission block, and
copyright information). For use with
SIG-ALTERNATE.CLS. Supported by ACM.}}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{2} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor Rahul Krishna\\ %\titlenote{North Carolina State University}\\
       \affaddr{North Carolina State University}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       %\affaddr{Wallamaloo, New Zealand}\\
       \email{rkrish11@ncsu.edu}
% 2nd. author
\alignauthor Anwesha Das \\%\titlenote{North Carolina State University.}\\
       \affaddr{North Carolina State University}\\
       %\affaddr{P.O. Box 1212}\\
       %\affaddr{Dublin, Ohio 43017-6221}\\
       \email{adas4@ncsu.edu}
% 3rd. author
%\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
%one who did all the really hard work.}\\
 %      \affaddr{The Th{\o}rv{\"a}ld Group}\\
  %     \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
  %     \affaddr{Hekla, Iceland}\\
  %     \email{larst@affiliation.org}
%\and  % use '\and' if you need 'another row' of author names
% 4th. author
%\alignauthor Lawrence P. Leipuner\\
 %      \affaddr{Brookhaven Laboratories}\\
  %     \affaddr{Brookhaven National Lab}\\
   %    \affaddr{P.O. Box 5000}\\
    %   \email{lleipuner@researchlabs.org}
% 5th. author
%\alignauthor Sean Fogarty\\
 %      \affaddr{NASA Ames Research Center}\\
 %      \affaddr{Moffett Field}\\
 %      \affaddr{California 94035}\\
 %      \email{fogartys@amesres.org}
% 6th. author
%\alignauthor Charles Palmer\\
 %      \affaddr{Palmer Research Laboratories}\\
  %     \affaddr{8600 Datapoint Drive}\\
  %     \affaddr{San Antonio, Texas 78229}\\
  %     \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{2nd Dec 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings. It is an {\em alternate} style which produces
a {\em tighter-looking} paper and was designed in response to
concerns expressed, by authors, over page-budgets.
It complements the document \textit{Author's (Alternate) Guide to
Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
This source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file. A compiled PDF version
is available on the web page to help you with the
`look and feel'.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
%\begin{CCSXML}
%<ccs2012>
 %<concept>
  %<concept_id>10010520.10010553.10010562</concept_id>
  %<concept_desc>Program Repair</concept_desc>
  %<concept_significance>500</concept_significance>
 %</concept>
 %<concept>
  %<concept_id>10010520.10010575.10010755</concept_id>
  %<concept_desc>Genprog</concept_desc>
  %<concept_significance>300</concept_significance>
 %</concept>
 %<concept>
  %<concept_id>10010520.10010553.10010554</concept_id>
  %<concept_desc>Multi-objective</concept_desc>
  %<concept_significance>100</concept_significance>
 %</concept>
 %<concept>
  %<concept_id>10003033.10003083.10003095</concept_id>
  %<concept_desc>Fitness</concept_desc>
  %<concept_significance>100</concept_significance>
 %</concept>
%</ccs2012>  
%\end{CCSXML}

%\ccsdesc[500]{Program Repair}
%\ccsdesc[300]{Genprog}
%\ccsdesc{Multi-objective}
%\ccsdesc[100]{Fitness}

%
% End generated code
%

%
%  Use this command to print the description
%
\printccsdesc

% We no longer use \terms command
%\terms{Theory}

\keywords{Program Repair; Genprog; Multi-objective}

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
and (1.9 cm [.75"]) left and right; specified column width
(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{Background}

\section{Evaluation}

\section{Discussion}

\section{Conclusion}

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.eps} files to be
displayable with \LaTeX.  If you work with pdf\LaTeX, use files in the
\textbf{.pdf} format.  Note that most modern \TeX\ system will convert
\textbf{.eps} to \textbf{.pdf} for you on the fly.  More details on
each of these is found in the \textit{Author's Guide}.

\begin{figure}
\centering
\includegraphics{fly}
\caption{A sample black and white graphic.}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=1in, width=1in]{fly}
\caption{A sample black and white graphic
that has been resized with the \texttt{includegraphics} command.}
\end{figure}

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption.
and don't forget to end the environment with
{figure*}, not {figure}!

\begin{figure*}
\centering
\includegraphics{flies}
\caption{A sample black and white graphic
that needs to span two columns of text.}
\end{figure*}

\begin{figure}
\centering
\includegraphics[height=1in, width=1in]{rosette}
\caption{A sample black and white graphic that has
been resized with the \texttt{includegraphics} command.}
\vskip -6pt
\end{figure}

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
%\section{Acknowledgments}

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{papers}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it.
You just add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start
of the document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The sig-alternate.cls file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.
%\balancecolumns % GM June 2007
% That's all folks!
\end{document}

### 2016-12-02 doc/final/manuscript.tex
Makefile Commit

@@
-% This is "sig-alternate.tex" V2.1 April 2013
-% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
-%
-% This example file demonstrates the use of the 'sig-alternate.cls'
-% V2.5 LaTeX2e document class file. It is for those submitting
-% articles to ACM Conference Proceedings WHO DO NOT WISH TO
-% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
-% The 'sig-alternate.cls' file will produce a similar-looking,
-% albeit, 'tighter' paper resulting in, invariably, fewer pages.
-%
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V2.5) produces:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) NO page numbers
-%
-% as against the acm_proc_article-sp.cls file which
-% DOES NOT produce 1) thru' 3) above.
-%
-% Using 'sig-alternate.cls' you have control, however, from within
-% the source .tex file, over both the CopyrightYear
-% (defaulted to 200X) and the ACM Copyright Data
-% (defaulted to X-XXXXX-XX-X/XX/XX).
-% e.g.
-% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
-% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
-%
-% ---------------------------------------------------------------------------------------------------------------
-% This .tex source is an example which *does* use
-% the .bib file (from which the .bbl file % is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission, you *NEED* to 'insert'
-% your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% ================= IF YOU HAVE QUESTIONS =======================
-% Questions regarding the SIGS styles, SIGS policies and
-% procedures, Conferences etc. should be sent to
-% Adrienne Griscti (griscti@acm.org)
-%
-% Technical questions _only_ to
-% Gerald Murray (murray@hq.acm.org)
-% ===============================================================
-%
-% For tracking purposes - this is V2.0 - May 2012
+\documentclass[]{sig-alternate}
+%\usepackage{stfloats}
+\usepackage{tikz}
+\def\firstcircle{(90:1.75cm) circle (2.5cm)}
+\def\secondcircle{(210:1.75cm) circle (2.5cm)}
+\def\thirdcircle{(330:1.75cm) circle (2.5cm)}
 
-\documentclass{sig-alternate-05-2015}
+\usepackage[framed]{ntheorem}
+\usepackage{framed}
+\usepackage{tikz}
+\usetikzlibrary{shadows}
+%\newtheorem{Lesson}{Lesson}
+\theoremclass{Lesson}
+\theoremstyle{break}
+
+% inner sep=10pt,
+\tikzstyle{thmbox} = [rectangle, rounded corners, draw=black,
+fill=Gray!20,  drop shadow={fill=black, opacity=1}]
+\newcommand\thmbox[1]{%
+	\noindent\begin{tikzpicture}%
+	\node [thmbox] (box){%
+		\begin{minipage}{.94\textwidth}%
+		\vspace{-3mm}#1\vspace{-3mm}%
+		\end{minipage}%
+	};%
+	\end{tikzpicture}}
+
+\let\theoremframecommand\thmbox
+\newshadedtheorem{lesson}{Research answer}
+
+\usepackage{booktabs}
+\usepackage{comment}
+\usepackage{cite}
+\usepackage{framed,graphicx,xcolor}
+\usepackage{multirow}
+\usepackage{rotating}
+%\usepackage{stfloats}
+\usepackage[shortlabels]{enumitem}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{url}
+\usepackage{balance}
+\usepackage{bigstrut}
+\newcommand{\bi}{\begin{itemize}}
+	\newcommand{\ei}{\end{itemize}}
+\newcommand{\be}{\begin{enumerate}}
+	\newcommand{\ee}{\end{enumerate}}
+\newcommand{\tion}[1]{\textsection\ref{sect:#1}}
+\newcommand{\tab}[1]{Figure~\ref{fig:#1}}
+\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
+%\setlist{nolistsep,leftmargin=5mm}
+%\usepackage[pdftex]{graphicx}
+% \usepackage{program}
+\newcommand{\Sample}{{\bf SAMPLE}}
+\newcommand{\PEEKING}{{\bf PEEKING2}}
+%\usepackage[table]{xcolor}
+\definecolor{darkgreen}{rgb}{0,0.3,0}
+\definecolor{Gray}{rgb}{0.88,1,1}
+\definecolor{Gray}{gray}{0.85}
+\definecolor{Blue}{RGB}{0,29,193}
+\usepackage{colortbl}
+\usepackage{picture}
+\usepackage{url}
+\usepackage{hyphenat}
+% \usepackage{hyperref}
+%\usepackage{listings}
+\DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator*{\argmax}{arg\,max}
+\definecolor{lightgray}{gray}{0.8}
+\definecolor{darkgray}{gray}{0.6}
+\definecolor{Gray}{gray}{0.95}
+\definecolor{LightGray}{gray}{0.975}
+
+\definecolor{Code}{rgb}{0,0,0}
+\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
+\definecolor{Numbers}{rgb}{0.5,0,0}
+\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
+\definecolor{Keywords}{rgb}{0,0,1}
+\definecolor{self}{rgb}{0,0,0}
+\definecolor{Strings}{rgb}{0,0.63,0}
+\definecolor{Comments}{rgb}{0,0.63,1}
+\definecolor{Comments}{rgb}{0.5,0.5,0.5}
+\definecolor{Backquotes}{rgb}{0,0,0}
+\definecolor{Classname}{rgb}{0,0,0}
+\definecolor{FunctionName}{rgb}{0,0,0}
+\definecolor{Operators}{rgb}{0,0,0}
+\definecolor{Background}{rgb}{1,1,1}
+\definecolor{lavenderpink}{rgb}{0.98, 0.68, 0.82}
+\definecolor{celadon}{rgb}{0.67, 0.88, 0.69}
+\newcommand{\G}{\cellcolor{green}}
+\newcommand{\Y}{\cellcolor{yellow}}
+
+\newcommand{\quart}[4]{\begin{picture}(80,4)%1
+	{\color{black}\put(#3,2){\circle*{4}}\put(#1,2){\line(1,0){#2}}}\end{picture}}
+\usepackage{url}
+
+\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45}
+\newenvironment{changed}{\par\color{MyDarkBlue}}{\par}
+%\newenvironment{changed}{\par}{\par}
+
+\newcommand{\ADD}[1]{\textcolor{MyDarkBlue}{{\bf #1}}}
+\usepackage{times}
+% \pagenumbering{arabic}
+\usepackage[splitrule]{footmisc} %% The splitrule option draws a full width
+%%rule above the continued part of the footnote as a visual cue to readers.
+\usepackage{balance}
+% \usepackage{flushend}
+\clubpenalty = 10000
+\widowpenalty = 10000
+\displaywidowpenalty = 10000
 
@@
 
-% Copyright
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
+     \definecolor{shadecolor}{gray}{0.9}
+     \conferenceinfo{CSC791:}{Automated Program Repair}
+     \title{Too Much Automation? The Bellwether Effect and Its Implications for Transfer Learning}
+     \numberofauthors{1}
+     \author{
+     	\alignauthor
+     	Rahul~Krishna \hspace{40pt} Anwesha~Das\\
+     	\affaddr{Computer Science, North Carolina State University, USA}\\
+     	{\{rkrish11, adas4\}@ncsu.edu}}
+     \maketitle
 
-% DOI
-\doi{10.475/123_4}
+		 \begin{abstract}
 
-% ISBN
-\isbn{123-4567-24-567/08/06}
+			 Automated Patch generation has garnered a lot of attention in the past decade.
+It has long been a elusive goal in software engineering.
+Automation has been a key research area and yet debugging/patch generation remains a largely manual process.
+One success story in this endeavor is \textit{GenProg} .
+In fact, GenProg, which is widely accepted as a promising tool by the research community, is now used as a baseline to compare other new techniques.
+Albeit popular, there is a general lack of consensus on the need for such complex tools to generate effective patches.
+While some researchers~\cite{leGoues12} opine that GenProg is quite effective in generating patches, given the existence of test cases, others \cite{qi2014, kim2013, arcuri2011} disagree.
+They say that it is quite unclear if the the efficacy of GenProg is merely due to its ``mutate'' operator or due to genetic programming.\\
 
-%Conference
-%\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
+			 \noindent{\bf Categories/Subject Descriptors:} D.2 [Software Engineering]; I.2
+        [Artificial Intelligence];
 
-%\acmPrice{\$15.00}
-
-%
-% --- Author Metadata here ---
-\conferenceinfo{ISSTA}{'17 Santa Barbara, CA USA}
-%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
-%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
-% --- End of Author Metadata ---
-
-\title{Multi-Objective Search in Automated Patch Generation
-\titlenote{(Produces the permission block, and
-copyright information). For use with
-SIG-ALTERNATE.CLS. Supported by ACM.}}
-%\subtitle{[Extended Abstract]
-%\titlenote{A full version of this paper is available as
-%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
-%\LaTeX$2_\epsilon$\ and BibTeX} at
-%\texttt{www.acm.org/eaddress.htm}}}
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
-
-\numberofauthors{2} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
-\author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
-\alignauthor Rahul Krishna\\ %\titlenote{North Carolina State University}\\
-       \affaddr{North Carolina State University}\\
-       %\affaddr{1932 Wallamaloo Lane}\\
-       %\affaddr{Wallamaloo, New Zealand}\\
-       \email{rkrish11@ncsu.edu}
-% 2nd. author
-\alignauthor Anwesha Das \\%\titlenote{North Carolina State University.}\\
-       \affaddr{North Carolina State University}\\
-       %\affaddr{P.O. Box 1212}\\
-       %\affaddr{Dublin, Ohio 43017-6221}\\
-       \email{adas4@ncsu.edu}
-% 3rd. author
-%\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
-%one who did all the really hard work.}\\
- %      \affaddr{The Th{\o}rv{\"a}ld Group}\\
-  %     \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
-  %     \affaddr{Hekla, Iceland}\\
-  %     \email{larst@affiliation.org}
-%\and  % use '\and' if you need 'another row' of author names
-% 4th. author
-%\alignauthor Lawrence P. Leipuner\\
- %      \affaddr{Brookhaven Laboratories}\\
-  %     \affaddr{Brookhaven National Lab}\\
-   %    \affaddr{P.O. Box 5000}\\
-    %   \email{lleipuner@researchlabs.org}
-% 5th. author
-%\alignauthor Sean Fogarty\\
- %      \affaddr{NASA Ames Research Center}\\
- %      \affaddr{Moffett Field}\\
- %      \affaddr{California 94035}\\
- %      \email{fogartys@amesres.org}
-% 6th. author
-%\alignauthor Charles Palmer\\
- %      \affaddr{Palmer Research Laboratories}\\
-  %     \affaddr{8600 Datapoint Drive}\\
-  %     \affaddr{San Antonio, Texas 78229}\\
-  %     \email{cpalmer@prl.com}
-}
-% There's nothing stopping you putting the seventh, eighth, etc.
-% author on the opening page (as the 'third row') but we ask,
-% for aesthetic reasons that you place these 'additional authors'
-% in the \additional authors block, viz.
-%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
-%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
-%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
-\date{2nd Dec 2016}
-% Just remember to make sure that the TOTAL number of authors
-% is the number that will appear on the first page PLUS the
-% number that will appear in the \additionalauthors section.
-
-\maketitle
-\begin{abstract}
-This paper provides a sample of a \LaTeX\ document which conforms,
-somewhat loosely, to the formatting guidelines for
-ACM SIG Proceedings. It is an {\em alternate} style which produces
-a {\em tighter-looking} paper and was designed in response to
-concerns expressed, by authors, over page-budgets.
-It complements the document \textit{Author's (Alternate) Guide to
-Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
-This source file has been written with the intention of being
-compiled under \LaTeX$2_\epsilon$\ and BibTeX.
-
-The developers have tried to include every imaginable sort
-of ``bells and whistles", such as a subtitle, footnotes on
-title, subtitle and authors, as well as in the text, and
-every optional component (e.g. Acknowledgments, Additional
-Authors, Appendices), not to mention examples of
-equations, theorems, tables and figures.
-
-To make best use of this sample document, run it through \LaTeX\
-and BibTeX, and compare this source code with the printed
-output produced by the dvi file. A compiled PDF version
-is available on the web page to help you with the
-`look and feel'.
+		 \keywords{Defect Prediction; Data Mining; Transfer learning}
 		 \end{abstract}
 
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
-%\begin{CCSXML}
-%<ccs2012>
- %<concept>
-  %<concept_id>10010520.10010553.10010562</concept_id>
-  %<concept_desc>Program Repair</concept_desc>
-  %<concept_significance>500</concept_significance>
- %</concept>
- %<concept>
-  %<concept_id>10010520.10010575.10010755</concept_id>
-  %<concept_desc>Genprog</concept_desc>
-  %<concept_significance>300</concept_significance>
- %</concept>
- %<concept>
-  %<concept_id>10010520.10010553.10010554</concept_id>
-  %<concept_desc>Multi-objective</concept_desc>
-  %<concept_significance>100</concept_significance>
- %</concept>
- %<concept>
-  %<concept_id>10003033.10003083.10003095</concept_id>
-  %<concept_desc>Fitness</concept_desc>
-  %<concept_significance>100</concept_significance>
- %</concept>
-%</ccs2012>  
-%\end{CCSXML}
+\section{Introduction}
 
-%\ccsdesc[500]{Program Repair}
-%\ccsdesc[300]{Genprog}
-%\ccsdesc{Multi-objective}
-%\ccsdesc[100]{Fitness}
+This issue was examined by Qi et at.~\cite{qi2014}.
+With their tool RSRepair (\underline{\textit{R}}andom-\underline{\textit{S}}earch \underline{\textit{Repair}}), they demonstrated the benefit of random search over GenProg.
 
-%
-% End generated code
-%
+It is my hypothesis that the lack of efficiency of GenProg in this area is not due to the failure of Genetic Algorithms (or any evolutionary computation scheme for that matter), but due to incorrect and perhaps even incomplete modeling of the search space.
 
-%
-%  Use this command to print the description
-%
-\printccsdesc
+As a motivating example consider Genetic Programming.
+The algorithm works by trying to maximize the ``fitness'' score.
+In this case, the number of passing test cases given a patch.
+RSRepair, on the other hand, considers either repair effectiveness (as measured by the number patch trials required) or repair efficiency (measured by the number of test case executions).
+It not hard to see that each of these objectives namely, the number of passing test cases, the repair effectiveness, and the repair efficiency, are all important.
+Perhaps some are more important than others, but they all play a crucial role nonetheless.
 
-% We no longer use \terms command
-%\terms{Theory}
+Therefore, I conjecture that the research in the area of automated patch generation will be best guided by modeling the domain as a multiobjective search problem with the aforementioned objectives.
+This, in my opinion, will allow us to leverage the wealth of research in Search Based Software Engineering (referred to henceforth as \textit{SBSE}).
+To this end, this project asks the following two research questions:
 
-\keywords{Program Repair; Genprog; Multi-objective}
+\subsubsection*{RQ1: Can automated patch generation be modeled as a multiobjective search problem?}
+Although it makes theoretical sense to view patch generation as containing multiple objectives, this question asks if it is practical to model it as such.
 
-\section{Introduction}
-The \textit{proceedings} are the records of a conference.
-ACM seeks to give these conference by-products a uniform,
-high-quality appearance.  To do this, ACM has some rigid
-requirements for the format of the proceedings documents: there
-is a specified format (balanced  double columns), a specified
-set of fonts (Arial or Helvetica and Times Roman) in
-certain specified sizes (for instance, 9 point for body copy),
-a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
-the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
-and (1.9 cm [.75"]) left and right; specified column width
-(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).
+\subsubsection*{RQ2: If yes, what is the best multiobjective search to generate patches automatically?}
+\label{rq2}
+If the answer to RQ1 is affirmative.
+This question aims to explore various multiobjective optimizers to identify the best algorithm.
+Specifically, this project will compare three standard SBSE techniques: NSGAII, MOEAD, Genetic Programming, using Random Search as a baseline.
+In addition to this, the usefulness of a promising new algorithm called SWAY\footnote{This algorithm is in current development by our research group}~\cite{chen2016sampling, nair2016accidental} will be also be investigated.
 
-The good news is, with only a handful of manual
-settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
-and {\texttt{\char'134 alignauthor}} commands, you have
-already used; another, {\texttt{\char'134 balancecolumns}}, will
-be used in your very last run of \LaTeX\ to ensure
-balanced column heights on the last page.}, the \LaTeX\ document
-class file handles all of this for you.
+\section{An Overview of Patch Generation}
 
-The remainder of this document is concerned with showing, in
-the context of an ``actual'' document, the \LaTeX\ commands
-specifically available for denoting the structure of a
-proceedings paper, rather than with giving rigorous descriptions
-or explanations of such commands.
+Generally, when a bug is reported, an automated program repair scheme undertakes the following three steps:
 
-\section{Background}
+\begin{enumerate}
+    \item \textit{Fault localization:}
+    These techniques are used to identify suspicious faulty code snippet that may a have caused the bug.
+
+    \item \textit{Patch Generation:}
+    Once faulty code snippet has been located, many candidate patches can be generated through the modifications to that code snippet, according to specific repair rules based on either evolutionary computation or code-based contracts.
+
+    \item \textit{Patch Validation:}
+    When a candidate patch has been produced, regression testing, inclusive of negative test cases (reproducing the fault) and positive test cases (characterizing the normal behaviors), is commonly used to validate the correctness of produced candidate patch.
+
+\end{enumerate}
+
+The above procedure can be iterated over and over again until some valid patch is found. Any patch passing all these test cases is considered valid.
+
+\input{aux_tex/measures.tex}
+\section{A (very) Brief Overview of Multiobjective Search}
+
+A search is the task of finding one or more solutions which satisfy one or more specified objectives.
+While a single-objective optimization involves a single objective function and a single solutions, a multiobjective optimization considers several objectives simultaneously.
+In reference to the current problem we have three competing objectives, all of which need to be maximized: (1) Number of passing test cases; (2) The repair effectiveness; and (3) The repair efficiency
+
+In such a case, a multiobjective optimizer generates a set of alternate solution with certain trade-offs.
+These are called \textit{Pareto Optimal Solutions}.
+The solutions, in our case, will be a set of valid patches that perform equally well when measured in terms of the three objectives.
+
+Multiobjective problems are usually complex, NP-Hard, and resource intensive.
+Although exact methods can be used, they consume prohibitively large amounts of time and memory.
+An alternative approach would be to make use of metaheuristic algorithms from RQ2.
+These approximate the Pareto frontier in a reasonable amount of time.
 
@@
 
-\section{Discussion}
+%\input{aux_tex/datasets.tex}
 
-\section{Conclusion}
+\subsection{Metrics}
+Figure \ref{fig:measure} highlights some of the preliminary performance evaluation measures we use to evaluate the algorithms.
+Please note that this will be expanded in future to accommodate other measures.
 
-\subsection{Tables}
-Because tables cannot be split across pages, the best
-placement for them is typically the top of the page
-nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and
-the table caption.  The contents of the table itself must go
-in the \textbf{tabular} environment, to
-be aligned properly in rows and columns, with the desired
-horizontal and vertical rules.  Again, detailed instructions
-on \textbf{tabular} material
-is found in the \textit{\LaTeX\ User's Guide}.
+\subsubsection{How to calculate them?}
+Calculating these metrics are well studied~\cite{deb2002fast, goel2010study}.
+We have an implementation in place that can readily give these metrics, given a set of ideal solutions (in this case, valid patches).
 
-Immediately following this sentence is the point at which
-Table 1 is included in the input file; compare the
-placement of the table here with the table in the printed
-dvi output of this document.
+\subsection{Datasets}
+The data set required for evaluating will be obtained from some recent work on GenProg~\cite{leGoues12}.
+My reading of the literature suggests that these dataset are the ``benchmarks'', used by several researchers~\cite{qi2014}.
+These are C programs with all the bugs reported reported in the historical versions as tabulated in Figure~\ref{fig:datasets}.
 
-\begin{table}
-\centering
-\caption{Frequency of Special Characters}
-\begin{tabular}{|c|c|l|} \hline
-Non-English or Math&Frequency&Comments\\ \hline
-\O & 1 in 1,000& For Swedish names\\ \hline
-$\pi$ & 1 in 5& Common in math\\ \hline
-\$ & 4 in 5 & Used in business\\ \hline
-$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-\hline\end{tabular}
-\end{table}
+\subsection{Tools}
+As for tools, it is worth noting that AST can be generated from C programs using a tool called CIL\footnote{https://sourceforge.net/projects/cil/}.
 
-To set a wider table, which takes up the whole width of
-the page's live area, use the environment
-\textbf{table*} to enclose the table's contents and
-the table caption.  As with a single-column table, this wide
-table will ``float" to a location deemed more desirable.
-Immediately following this sentence is the point at which
-Table 2 is included in the input file; again, it is
-instructive to compare the placement of the
-table here with the table in the printed dvi
-output of this document.
+\subsection{Analysis Plan}
+To provide a more comprehensive comparison, the optimizers will be ranked ranked statistically. To do this, I shall use the Scott-Knott procedure recommended by Mittas \& Angelis\cite{mittas13}.
 
-\begin{table*}
-\centering
-\caption{Some Typical Commands}
-\begin{tabular}{|c|c|l|} \hline
-Command&A Number&Comments\\ \hline
-\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
-\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
-\texttt{{\char'134}table}& 300 & For tables\\ \hline
-\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
-\end{table*}
-% end the environment with {table*}, NOTE not {table}!
+This method sorts a list of $l$ treatments with $ls$ measurements by their median
+score. It then
+splits $l$ into sub-lists $m,n$ in order to maximize the expected value of
+differences  in the observed performances
+before and after divisions. E.g. for lists $l,m,n$ of size $ls,ms,ns$ where $l=m\cup n$:
+\[E(\Delta)=\frac{ms}{ls}abs(m.\mu - l.\mu)^2 + \frac{ns}{ls}abs(n.\mu - l.\mu)^2\]
+Scott-Knott then applies some statistical hypothesis test $H$ to check
+if $m,n$ are significantly different. If so, Scott-Knott then recurses on each division.
 
-\subsection{Figures}
-Like tables, figures cannot be split across pages; the
-best placement for them
-is typically the top or the bottom of the page nearest
-their initial cite.  To ensure this proper ``floating'' placement
-of figures, use the environment
-\textbf{figure} to enclose the figure and its caption.
+\section{Proposed Timeline}
 
-This sample document contains examples of \textbf{.eps} files to be
-displayable with \LaTeX.  If you work with pdf\LaTeX, use files in the
-\textbf{.pdf} format.  Note that most modern \TeX\ system will convert
-\textbf{.eps} to \textbf{.pdf} for you on the fly.  More details on
-each of these is found in the \textit{Author's Guide}.
-
-\begin{figure}
-\centering
-\includegraphics{fly}
-\caption{A sample black and white graphic.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[height=1in, width=1in]{fly}
-\caption{A sample black and white graphic
-that has been resized with the \texttt{includegraphics} command.}
-\end{figure}
-
-As was the case with tables, you may want a figure
-that spans two columns.  To do this, and still to
-ensure proper ``floating'' placement of tables, use the environment
-\textbf{figure*} to enclose the figure and its caption.
-and don't forget to end the environment with
-{figure*}, not {figure}!
-
-\begin{figure*}
-\centering
-\includegraphics{flies}
-\caption{A sample black and white graphic
-that needs to span two columns of text.}
-\end{figure*}
-
-\begin{figure}
-\centering
-\includegraphics[height=1in, width=1in]{rosette}
-\caption{A sample black and white graphic that has
-been resized with the \texttt{includegraphics} command.}
-\vskip -6pt
-\end{figure}
-
-\subsection{Theorem-like Constructs}
-Other common constructs that may occur in your article are
-the forms for logical constructs like theorems, axioms,
-corollaries and proofs.  There are
-two forms, one produced by the
-command \texttt{{\char'134}newtheorem} and the
-other by the command \texttt{{\char'134}newdef}; perhaps
-the clearest and easiest way to distinguish them is
-to compare the two in the output of this sample document:
-
-This uses the \textbf{theorem} environment, created by
-the\linebreak\texttt{{\char'134}newtheorem} command:
-\newtheorem{theorem}{Theorem}
-\begin{theorem}
-Let $f$ be continuous on $[a,b]$.  If $G$ is
-an antiderivative for $f$ on $[a,b]$, then
-\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
-\end{theorem}
-
-The other uses the \textbf{definition} environment, created
-by the \texttt{{\char'134}newdef} command:
-\newdef{definition}{Definition}
-\begin{definition}
-If $z$ is irrational, then by $e^z$ we mean the
-unique number which has
-logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
-\end{definition}
-
-Two lists of constructs that use one of these
-forms is given in the
-\textit{Author's  Guidelines}.
-
-There is one other similar construct environment, which is
-already set up
-for you; i.e. you must \textit{not} use
-a \texttt{{\char'134}newdef} command to
-create it: the \textbf{proof} environment.  Here
-is a example of its use:
-\begin{proof}
-Suppose on the contrary there exists a real number $L$ such that
-\begin{displaymath}
-\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-\end{displaymath}
-Then
-\begin{displaymath}
-l=\lim_{x\rightarrow c} f(x)
-= \lim_{x\rightarrow c}
-\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
-= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-\frac{f(x)}{g(x)} = 0\cdot L = 0,
-\end{displaymath}
-which contradicts our assumption that $l\neq 0$.
-\end{proof}
-
-Complete rules about using these environments and using the
-two different creation commands are in the
-\textit{Author's Guide}; please consult it for more
-detailed instructions.  If you need to use another construct,
-not listed therein, which you want to have the same
-formatting as the Theorem
-or the Definition\cite{salas:calculus} shown above,
-use the \texttt{{\char'134}newtheorem} or the
-\texttt{{\char'134}newdef} command,
-respectively, to create it.
-
-%\end{document}  % This is where a 'short' article might terminate
-
-%ACKNOWLEDGMENTS are optional
-%\section{Acknowledgments}
-
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
-\bibliographystyle{abbrv}
-\bibliography{papers}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
-%
-%APPENDICES are optional
-%\balancecolumns
-\appendix
-%Appendix A
-\section{Headings in Appendices}
-The rules about hierarchical headings discussed above for
-the body of the article are different in the appendices.
-In the \textbf{appendix} environment, the command
-\textbf{section} is used to
-indicate the start of each Appendix, with alphabetic order
-designation (i.e. the first is A, the second B, etc.) and
-a title (if you include one).  So, if you need
-hierarchical structure
-\textit{within} an Appendix, start with \textbf{subsection} as the
-highest level. Here is an outline of the body of this
-document in Appendix-appropriate form:
-\subsection{Introduction}
-\subsection{The Body of the Paper}
-\subsubsection{Type Changes and  Special Characters}
-\subsubsection{Math Equations}
-\paragraph{Inline (In-text) Equations}
-\paragraph{Display Equations}
-\subsubsection{Citations}
-\subsubsection{Tables}
-\subsubsection{Figures}
-\subsubsection{Theorem-like Constructs}
-\subsubsection*{A Caveat for the \TeX\ Expert}
-\subsection{Conclusions}
-\subsection{Acknowledgments}
-\subsection{Additional Authors}
-This section is inserted by \LaTeX; you do not insert it.
-You just add the names and information in the
-\texttt{{\char'134}additionalauthors} command at the start
-of the document.
-\subsection{References}
-Generated by bibtex from your ~.bib file.  Run latex,
-then bibtex, then latex twice (to resolve references)
-to create the ~.bbl file.  Insert that ~.bbl file into
-the .tex source file and comment out
-the command \texttt{{\char'134}thebibliography}.
-% This next section command marks the start of
-% Appendix B, and does not continue the present hierarchy
-\section{More Help for the Hardy}
-The sig-alternate.cls file itself is chock-full of succinct
-and helpful comments.  If you consider yourself a moderately
-experienced to expert user of \LaTeX, you may find reading
-it useful but please remember not to change it.
-%\balancecolumns % GM June 2007
-% That's all folks!
+Figure \ref{time} highlights the proposed timeline for the tasks undertaken in the project.
+Please note again that this subject to change, please see https://github.com/ai-se/spatch/milestones for the latest milestone progress.\\
+\pagebreak
+\bibliographystyle{unsrt}
+\bibliography{References}
 \end{document}

### 2016-12-03 doc/final/manuscript.tex
Makefile Commit

@@
-\documentclass[]{sig-alternate}
+\documentclass{sig-alternate}
 %\usepackage{stfloats}
@@
 \def\thirdcircle{(330:1.75cm) circle (2.5cm)}
-
+\usepackage{graphicx}
 \usepackage[framed]{ntheorem}
@@
 	\newcommand{\ee}{\end{enumerate}}
-\newcommand{\tion}[1]{\textsection\ref{sect:#1}}
-\newcommand{\tab}[1]{Figure~\ref{fig:#1}}
+\newcommand{\tion}[1]{\textsection\ref{#1}}
+\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
 \newcommand{\eq}[1]{Equation~\ref{eq:#1}}
@@
 \newcommand{\Y}{\cellcolor{yellow}}
-
+%\usepackage{parskip}
+\setlength{\parskip}{1ex} % 1ex plus 0.5ex minus 0.2ex}
+%\setlength{\parindent}{0pt}
 \newcommand{\quart}[4]{\begin{picture}(80,4)%1
@@
 \displaywidowpenalty = 10000
+\newfont{\mycrnotice}{ptmr8t at 7pt}
+\newfont{\myconfname}{ptmri8t at 7pt}
+\let\crnotice\mycrnotice%
+\let\confname\myconfname%
 
@@
      \definecolor{shadecolor}{gray}{0.9}
-     \conferenceinfo{CSC791:}{Automated Program Repair}
-     \title{Too Much Automation? The Bellwether Effect and Its Implications for Transfer Learning}
+
+     \title{A Case For Multi-Objective Search In Automated Program Repair}
      \numberofauthors{1}
@@
      	{\{rkrish11, adas4\}@ncsu.edu}}
+      \permission{Permission to make digital or hard copies of all or part of
+        this work for personal or classroom use is granted without fee provided 
+        that copies are not made or distributed for profit or commercial advantage 
+        and that copies bear this notice and the full citation on the first page. 
+        Copyrights for components of this work owned by others than the author(s) 
+        must be honored. Abstracting with credit is permitted. To copy otherwise, 
+        or republish, to post on servers or to redistribute to lists, requires 
+        prior specific permission and/or a fee. Request permissions from 
+        Permissions@acm.org.}
+      \conferenceinfo{CSC791:}{Automated Program Repair\\
+        {\mycrnotice{Copyright is held by the owner/author(s). Publication rights 
+            licensed to ACM.}}}
+      \copyrightetc{ACM \the\acmcopyr}
+      \crdata{123-4-5679-10/11/12\ ...\$00.00.\\
+        http://dx.doi.org/}
      \maketitle
@@
 Automation has been a key research area and yet debugging/patch generation remains a largely manual process.
-One success story in this endeavor is \textit{GenProg} .
-In fact, GenProg, which is widely accepted as a promising tool by the research community, is now used as a baseline to compare other new techniques.
+One success story in this endeavor is \textit{GenProg}.
+In fact, GenProg, widely accepted as a promising tool by the research community, is now used as a baseline to compare other new techniques.
 Albeit popular, there is a general lack of consensus on the need for such complex tools to generate effective patches.
-While some researchers~\cite{leGoues12} opine that GenProg is quite effective in generating patches, given the existence of test cases, others \cite{qi2014, kim2013, arcuri2011} disagree.
-They say that it is quite unclear if the the efficacy of GenProg is merely due to its ``mutate'' operator or due to genetic programming.\\
-
+While some researchers opine that GenProg is quite effective in generating patches, given the existence of test cases, others disagree.
+They say that it is quite unclear if the efficacy of GenProg is merely due to its ``mutate'' operator or due to genetic programming.
+In this report we set out to these hypothesis.
+We conjectured that GenProg would be just as efficient if the core search strategy i.e., genetic programming, is replaced by other variants of genetic algorithms.
+In specific, we used NSGA-II, a very popular variant of genetic algorithm that has been extensively used and studied in search based software engineering.
+In addition to this, we also hypothesized that it is possible to generate better patches by converting genetic programming from it's current single objective form to a multiobjective search.
+Our findings contradict researchers claims that the success of genprog is the ``mutate'' operation.
+We show that genetic programming plays a critical role in the success of GenProg.
+Additionally, we show that by increasing the number of objectives used in fitness evaluation form one to two, GenProg succeeds in producing valid patches while also performing a more expansive search.\\
+%       \newpage
 			 \noindent{\bf Categories/Subject Descriptors:} D.2 [Software Engineering]; I.2
         [Artificial Intelligence];
-
 	     \keywords{Defect Prediction; Data Mining; Transfer learning}
      \end{abstract}  		
-
 \section{Introduction}
 
-This issue was examined by Qi et at.~\cite{qi2014}.
+Maintaining released software is a rather difficult, time- consuming, and a manual
+process.
+In their book, Seacord et al.~\cite{seacord:2003:MLS:599767} place software maintenance, traditionally defined as any modification made on a system after its delivery, at 90\% of the total cost of a typical software project.
+The literature on software maintenance is expansive.
+They all note that modifying existing code consumes a significant amount of maintenance effort.
+Anvik et al.~\cite{anvik2005coping} find that the number of outstanding software defects usually outnumbers the available resources to address them.
+Similarly, Liblit et al.~\cite{liblit2003bug} remark that several software systems are shipped to known and unknown bugs because of the lack of resources.
+
+To alleviate the load on developers working on these issues automated patch generation has been proposed.
+Over the past decade research on this front has gained a lot of traction in the software engineering community.
+Specifically, tools that leverage evolution computation strategies, like GenProg~\cite{leGoues12}, have seen tremendous amounts of success.
+
+Although widely accepted as an excellent tool, researchers have questioned the reported lack of efficiency these tools.
+Researchers also generally disagree on if evolutionary computation is a good candidate for patch generation.
+For instance, several researchers~\cite{qi2014, kim2013, arcuri2011} say that it is quite unclear if the the efficacy (or lack thereof) of GenProg is due to its ``mutate'' operator or due to genetic programming.
+This issue was further examined by Qi et at.~\cite{qi2014}.
 With their tool RSRepair (\underline{\textit{R}}andom-\underline{\textit{S}}earch \underline{\textit{Repair}}), they demonstrated the benefit of random search over GenProg.
 
-It is my hypothesis that the lack of efficiency of GenProg in this area is not due to the failure of Genetic Algorithms (or any evolutionary computation scheme for that matter), but due to incorrect and perhaps even incomplete modeling of the search space.
+A motivation for this study was our hypothesis that the lack of efficiency of GenProg, in some cases, in this area is not due to the failure of Genetic Algorithms (or any evolutionary computation scheme for that matter), but due to incorrect and perhaps even incomplete modeling of the search space.
+We therefore propose the use of multiobjective search in automated program repair which extends the original single objective GenProg by adding additional objectives to satisfy the fitness function.
+Additionally, to verify if the success of GenProg is indeed due to genetic programming and not mutation/crossover operations, we study to performance of NGSAII~\cite{nsgaii}.
+It is also worth noting that, to be best of our knowledge, this is the first attempt to study multiobjective patch generation in automated program repair.
 
-As a motivating example consider Genetic Programming.
-The algorithm works by trying to maximize the ``fitness'' score.
+With this premise, the rest of this paper explores, in greater detail, the impact of multi-objective evolutionary algorithms in automated program repair.
+The report is structured as follows: \tion{rq} highlights the research questions that will be answered; \tion{prelim} presents a brief summary of the domain and multi-objective search; \tion{eval}
+presents our evaluation strategy; \tion{results} presents the experimental result; this is followed by \tion{discuss} that discusses our findings; and finally, \tion{conclusions} presents the conclusion and guides readers to potential future work.
+
+\section{Research Questions}
+\label{rq}
+We conjecture that one way to further the research in the area of automated patch generation may be by modeling the domain as a multiobjective search problem.
+Consider genetic programming --- the algorithm works by trying to maximize the ``fitness'' score.
 In this case, the number of passing test cases given a patch.
-RSRepair, on the other hand, considers either repair effectiveness (as measured by the number patch trials required) or repair efficiency (measured by the number of test case executions).
+Algorithms like RSRepair, on the other hand, considers either repair effectiveness (as measured by the number patch trials required) or repair efficiency (measured by the number of test case executions).
 It not hard to see that each of these objectives namely, the number of passing test cases, the repair effectiveness, and the repair efficiency, are all important.
@@
 
-Therefore, I conjecture that the research in the area of automated patch generation will be best guided by modeling the domain as a multiobjective search problem with the aforementioned objectives.
-This, in my opinion, will allow us to leverage the wealth of research in Search Based Software Engineering (referred to henceforth as \textit{SBSE}).
-To this end, this project asks the following two research questions:
+Converting to multi-objective fitness evaluation, will allow us to leverage the wealth of research in Search Based Software Engineering (referred to henceforth as \textit{SBSE}).
+To this end, in our study we ask the following research questions:
 
-\subsubsection*{RQ1: Can automated patch generation be modeled as a multiobjective search problem?}
+\subsection*{RQ1: Can automated patch generation be modeled as a multiobjective search problem?}
+\label{rq1}
 Although it makes theoretical sense to view patch generation as containing multiple objectives, this question asks if it is practical to model it as such.
 
-\subsubsection*{RQ2: If yes, what is the best multiobjective search to generate patches automatically?}
+\subsection*{RQ2: If yes, how does single objective GP compare to multiobjective GP?}
 \label{rq2}
 If the answer to RQ1 is affirmative.
-This question aims to explore various multiobjective optimizers to identify the best algorithm.
-Specifically, this project will compare three standard SBSE techniques: NSGAII, MOEAD, Genetic Programming, using Random Search as a baseline.
-In addition to this, the usefulness of a promising new algorithm called SWAY\footnote{This algorithm is in current development by our research group}~\cite{chen2016sampling, nair2016accidental} will be also be investigated.
+This question aims to extend a simple single objective genetic programming algorithm to multiobjective search.
+Then, we reflect on the patches generated by each algorithm to study their quality.
 
-\section{An Overview of Patch Generation}
+\subsection*{RQ3: Can we replace genetic programming by some other genetic algorithm?}
+\label{rq3}
+Assuming that we can answer RQ2, this question would be a natural extension to that.
+Here we ask what would happen if we used a different multiobjective optimizer in place of genetic programing.
+With this, we seek to validate (or perhaps deprecate) certain claims of studies by Qi et al.~\cite{qi2014}.
+They consider that the success of GenProg is due to the ``mutate'' operation of evolutionary algorithms and not genetic programming.
 
-Generally, when a bug is reported, an automated program repair scheme undertakes the following three steps:
+\input{figs/gp.tex}
 
-\begin{enumerate}
-    \item \textit{Fault localization:}
-    These techniques are used to identify suspicious faulty code snippet that may a have caused the bug.
+We believe this to be untrue and to verify our opinion we replace GP with NSGAII~\cite{nsgaii}.
+NSGAII is a incredibly popular variant of GA (18000+ citations).
+NSGAII consists of a novel sort algorithm that enables it identify better solutions and to converge at these solution much faster.
 
-    \item \textit{Patch Generation:}
-    Once faulty code snippet has been located, many candidate patches can be generated through the modifications to that code snippet, according to specific repair rules based on either evolutionary computation or code-based contracts.
+\section{Methods and Materials}
+\label{prelim}
+Generally, when a bug is reported, an automated program repair tool based on a evolutionary algorithm undertakes a set of standard steps as endorsed by LeGoues et al~\cite{Goues}\footnote{Unfortunately, space limitations do not permit a detailed explanation of each of these steps, so this will brief.}.
 
-    \item \textit{Patch Validation:}
-    When a candidate patch has been produced, regression testing, inclusive of negative test cases (reproducing the fault) and positive test cases (characterizing the normal behaviors), is commonly used to validate the correctness of produced candidate patch.
+\input{figs/nsgaii.tex}
+\subsection{Search Strategy}
 
-\end{enumerate}
+GenProg proposes that use of an iterated stochastic search technique, to search for program repairs.
+Indeed, the search space comprising of possible repairs is extremely large, and any search algorithm would be required employ these four strategies to be a practical option: (1) generate coarse-grained, statement-level patches to reduce search space size; (2) implement fault localization to focus edit locations; (3) access existing code to provide the seed of new repairs; and (4) use a fitness approximation to cull bad patches.
 
-The above procedure can be iterated over and over again until some valid patch is found. Any patch passing all these test cases is considered valid.
+In this paper, we discuss to such search strategies: GP and NSGA-II.
+Both of these are in fact variants of standard genetic algorithm.
+Motivated by studies on genetics, GA appeared in early 60s as a potential meta-heuristic search strategy.
+The rest of this subsection provides a very brief introduction to multiobjective search and the two algorithms\footnote{Interested readers are encouraged to read~\cite{clever} for a more in-depth discussion of these and other similar algorithms}.
 
-\input{aux_tex/measures.tex}
-\section{A (very) Brief Overview of Multiobjective Search}
+\subsubsection{An Overview of Multiobjective Search}
+\label{mos}
+A multiobjective search is the task of finding solutions which satisfy two or more specified objectives.
+While a single-objective optimization involves a single objective function and a single solution, a multiobjective optimization considers several objectives simultaneously.
 
-A search is the task of finding one or more solutions which satisfy one or more specified objectives.
-While a single-objective optimization involves a single objective function and a single solutions, a multiobjective optimization considers several objectives simultaneously.
-In reference to the current problem we have three competing objectives, all of which need to be maximized: (1) Number of passing test cases; (2) The repair effectiveness; and (3) The repair efficiency
+In context of the current problem we have two potentially conflicting objectives: 
+\be
+\item Total number of failing test cases: needs to be minimized; and 
+\item Number of test case executions before the first failure: needs to be maximized.
+\ee
 
-In such a case, a multiobjective optimizer generates a set of alternate solution with certain trade-offs.
+\input{figs/gp_ex.tex}
+
+\input{figs/results.tex}
+In such a case, a multiobjective optimizer generates a set of alternate solutions with certain trade-offs.
 These are called \textit{Pareto Optimal Solutions}.
-The solutions, in our case, will be a set of valid patches that perform equally well when measured in terms of the three objectives.
+The solutions, in our case, will be a set of valid patches that perform equally well when measured in terms of the two objectives listed above.
 
@@
 Although exact methods can be used, they consume prohibitively large amounts of time and memory.
-An alternative approach would be to make use of metaheuristic algorithms from RQ2.
+An alternative approach would be to make use of meta-heuristic algorithms from RQ3.
 These approximate the Pareto frontier in a reasonable amount of time.
 
+\subsubsection{Genetic Programming}
+
+The Genetic Programming algorithm is inspired by population genetics (including heredity and gene frequencies), and evolution at the population level, as well as the Mendelian understanding of the structure (such as chromosomes, genes, alleles) and mechanisms (such as crossover and mutation).
+
+In the context of program repair, the objective of the Genetic Programming algorithm is to use induction to search potential patches.
+This is achieved by using evolutionary operators on candidate programs and their Abstract Syntax Trees to improve the adaptive fit between the population of candidate programs and an objective function.
+An assessment of a candidate solution involves the execution of given test cases counting the number of failures with a given patch.
+
+High-level pseudocode for GenProg's main GP loop is shown in \fig{gp_pseudo}; it closely resembles~\cite{Goues}.
+Fitness is measured as a weighted average of the positive (i.e., initially passing, encoding required functionality) and negative (i.e., initially failing, encoding a defect) test cases.
+The goal is to produce a candidate patch that causes the original program to pass all test cases.
+In this paper, each individual, or variant, is represented as a repair patch stored and operated as an AST.
+
+\subsubsection{NSGA-II}
+
+The objective of NSGA-II algorithm is to improve the adaptive fit of a population of candidate solutions to a Pareto front (see section~\ref{mos} for definition) constrained by a set of objective functions.
+The algorithm uses an evolutionary process with surrogates for evolutionary operators including selection, genetic crossover, and genetic mutation.
+The population is sorted into a hierarchy of sub-populations based on the ordering of Pareto dominance.
+Similarity between members of each sub-group is evaluated on the Pareto front, and the resulting groups and similarity measures are used to promote a diverse front of ``non-dominated'' solutions.
+
+\fig{nsgaII} provides a pseudocode listing of the Non-dominated Sorting Genetic Algorithm II (NSGA-II) for minimizing a cost function.
+The \texttt{SortByRankAndDistance} function orders the population into a hierarchy of non-dominated Pareto fronts.
+The \texttt{CrowdingDistanceAssignment} calculates the average distance between members of each front on the front
+itself.
+
+\subsection{A Note on Patch Representation}
+\label{patch_rep}
+There are two fundamental differences between NSGA-II and GP.
+The first is of course, the nature of sort after each generation.
+NSGA-II uses a novel non-dominated sorting followed by an elite sampling to pick members that are retained in the population for the next iteration of the algorithm.
+GP on the other hand uses a simple \texttt{quicksort} followed by top-N sampling to pick members for the next iteration of the algorithm.
+
+A more important distinction lies in the patch representation used by both these algorithms.
+NSGA-II converts the code in flattened representation.
+In a ``flat representation'' every line/expression is considered independent of every other line/expression.
+Mutations/Crossovers can affect any line.
+This is quite dangerous for obvious reasons.
+
+GP on the other hand takes a tree-based approach for code representation.
+It makes use of ASTs to represent the code.
+AST by nature respect code hierarchies and interdependencies.
+Thus, any mutation/crossover will not only affect a line, but will also affect the so-called children of that statement.
+A simple example is shown in ~\fig{gp_ex} for reference.
+
+\subsection{Fault Localization}
+After the search strategy is determined.
+An automated program repair scheme uses some form of fault localization to locate faults in a given code.
+GenProg\footnote{Note that when we say GenProg we refer to it as a scheme.
+All statements made about it apply to Genetic Programming and NSGA-II} focuses repair efforts on statements that are visited by the negative test cases, biased heavily towards those that are not also visited by positive test cases.
+
+\subsection{Patch Generation}
+Once faulty code snippet has been located, many candidate patches can be generated through the modifications to that code snippet, according to specific repair rules based on either evolutionary computation or code-based contracts.
+In the context of search, these would be solutions on the Pareto Frontier.
+Patches are represented as the source of insertion/replacement code pointed to on an AST (in the case of GP) or as line modifications to be performed (in case of NSGA-II).
+
+\subsection{Patch Validation}
+When a candidate patch has been produced it is represented as a new AST (or new set of lines/expressions in the case of NSGA-II).
+The code is then modified to reflect these recommendations.
+This is followed by regression testing, inclusive of negative test cases (reproducing the fault) and positive test cases (characterizing the normal behaviors), is commonly used to validate the correctness of produced candidate patch.
+The above procedure can be iterated over and over again until some valid patch is found.
+Any patch passing all these test cases is considered valid.
+
+The fitness of a patch is a quantitative measure which is obtained by counting the following two measures: (1) Number of test case failure for a patch; and (2) Number of successful evaluations before the first test case failure.
+
+%\input{aux_tex/measures.tex}
+
 \section{Evaluation}
+\label{eval}
+\subsubsection{Number of fixes}
 
-%\input{aux_tex/datasets.tex}
+This measure looks at the total number of bug fixes offered by the program. A successful program repair tool would at least generate one patch. A powerful tool should patch everything.
 
-\subsection{Metrics}
-Figure \ref{fig:measure} highlights some of the preliminary performance evaluation measures we use to evaluate the algorithms.
-Please note that this will be expanded in future to accommodate other measures.
+\subsubsection{Evaluation Time}
 
-\subsubsection{How to calculate them?}
-Calculating these metrics are well studied~\cite{deb2002fast, goel2010study}.
-We have an implementation in place that can readily give these metrics, given a set of ideal solutions (in this case, valid patches).
+As highlighted previously, multiobjective search algorithms are notorious for their impractically large run times.
+It is then important to measure how long a program takes to terminate.
+If the time taken is much larger than how much a human would take, it necessitates improving the algorithms or relaxing fitness criteria.
 
-\subsection{Datasets}
-The data set required for evaluating will be obtained from some recent work on GenProg~\cite{leGoues12}.
-My reading of the literature suggests that these dataset are the ``benchmarks'', used by several researchers~\cite{qi2014}.
-These are C programs with all the bugs reported reported in the historical versions as tabulated in Figure~\ref{fig:datasets}.
+\subsubsection{Patch variance}
 
-\subsection{Tools}
-As for tools, it is worth noting that AST can be generated from C programs using a tool called CIL\footnote{https://sourceforge.net/projects/cil/}.
+This measure is used to study the nature of patches generated by a search algorithm.
+It is entirely possible that a bug may be fixed in more that one way.
+Then, an method that can explore a much larger search space would be an enticing alternative to a narrow search scheme.
+\input{figs/results2.tex}
+\section{Experimental Results}
+\label{results}
 
-\subsection{Analysis Plan}
-To provide a more comprehensive comparison, the optimizers will be ranked ranked statistically. To do this, I shall use the Scott-Knott procedure recommended by Mittas \& Angelis\cite{mittas13}.
+\subsection*{RQ1: Can automated patch generation be modeled as a multiobjective search problem?}
+To answer this question, we modeled GP as a two objective optimization and compared it with a single object GP that was available to us.
+The results we quite interesting, we found that a multiobjective GP fixed all the lines as the single objective GP.
+A sample \texttt{FaultFile} and \texttt{FixFile} are shown in Figure 6 and Figure 7.
+Note that in both the cases we obtained the exact same fixes in all the test programs.
+Thus, for parsimony's sake, we chose to report only one.
 
-This method sorts a list of $l$ treatments with $ls$ measurements by their median
-score. It then
-splits $l$ into sub-lists $m,n$ in order to maximize the expected value of
-differences  in the observed performances
-before and after divisions. E.g. for lists $l,m,n$ of size $ls,ms,ns$ where $l=m\cup n$:
-\[E(\Delta)=\frac{ms}{ls}abs(m.\mu - l.\mu)^2 + \frac{ns}{ls}abs(n.\mu - l.\mu)^2\]
-Scott-Knott then applies some statistical hypothesis test $H$ to check
-if $m,n$ are significantly different. If so, Scott-Knott then recurses on each division.
+Therefore, this research question may be answered as follows:
+\begin{lesson}
+Yes. Automated patch generation \textbf{can} indeed be modeled as a multiobjective search problem.
+\end{lesson}
 
-\section{Proposed Timeline}
+\subsection*{RQ2: If yes, how does single objective GP compare to multiobjective GP?}
+To answer this question, we study the evaluation time and test case variants.
+\fig{res_1} shows that in terms of runtime multiobjective GP is only slightly larger than traditional GP.
+But, more interestingly \fig{res_2} shows that multiobjective GP has a \textit{significantly  larger} variance than traditional GP.
+This is particularly interesting as it shows that multiobjective GP performs a more expansive search while looking for candidate patches.
 
-Figure \ref{time} highlights the proposed timeline for the tasks undertaken in the project.
-Please note again that this subject to change, please see https://github.com/ai-se/spatch/milestones for the latest milestone progress.\\
-\pagebreak
+Keeping these findings in view, this research question may be answered as follows.
+\begin{lesson}
+   Multiobjective GP is \textbf{significantly better} than simple GP in terms of patch variance. While also being \textbf{no worse} than simple GP in terms of evaluation times.
+\end{lesson}
+
+\subsection*{Can we replace genetic programming by some other genetic algorithm?}
+To answer this question, we replaced GP with NSGA-II.
+We found, from ~\fig{res_1} and \fig{res_2}, that in addition to exorbitantly large runtimes in several cases, it fares no better in terms of variance.
+More importantly, NSGA-II fails to find any patch at all!
+Our findings are that this is due to a rather naive approach to patch representation used by NSGA-II, discussed in detail in \ref{patch_rep}.
+
+Our findings lead to the following research answer:
+\begin{lesson}
+  Replacing GP with another genetic algorithm without a good patch representation approach is not advised.
+\end{lesson}
+
+\section{Discussions}
+\label{discuss}
+
+This report made an attempt to validate the efficacy of GP (as a multiobjective search) and the nature of mutate operations in GenProg.
+From RQ1 and RQ2 we note that, converting single objective GP to a multiobjective GP offers a significant benefits in that it performs a more expansive search for patches.
+From the outcome of RQ3 we find that GP owing to their tree-based mutation structure play a very important role in the operation of patch generation.
+Additionally, we found that NSGA-II failed to generate any patch, and this was due to the flattened representation of patches used by NSGA-II.
+
+\section{Future Work}
+\label{conclusions}
+In conclusion, our study introduced the use of multiple objectives in patch generation. It also show the importance of patch representation when performing a multiobjective search for patches.
+
+As for future work, efforts must be taken to update the notation of patches prior to performing search.
+Also, other novel search strategies that use both GP and Non-dominated sort may be explored.
+In addition to this, the usefulness of a promising new algorithm called SWAY\footnote{This algorithm is in current development by our research group}~\cite{chen2016sampling, nair2016accidental} may be also be investigated.
+
 \bibliographystyle{unsrt}
-\bibliography{References}
+\bibliography{references}
 \end{document}

### 2016-12-03 doc/final/manuscript.tex
Makefile Commit

@@
 			 Automated Patch generation has garnered a lot of attention in the past decade.
-It has long been a elusive goal in software engineering.
+It has long been an elusive goal in software engineering.
 Automation has been a key research area and yet debugging/patch generation remains a largely manual process.
@@
 In this report we set out to these hypothesis.
-We conjectured that GenProg would be just as efficient if the core search strategy i.e., genetic programming, is replaced by other variants of genetic algorithms.
+We tried to study if GenProg would be just as efficient if the core search strategy i.e., genetic programming, is replaced by other variants of genetic algorithms.
 In specific, we used NSGA-II, a very popular variant of genetic algorithm that has been extensively used and studied in search based software engineering.
@@
 
-Maintaining released software is a rather difficult, time- consuming, and a manual
+Maintaining released software is a rather difficult, time-consuming, and a manual
 process.
@@
 Anvik et al.~\cite{anvik2005coping} find that the number of outstanding software defects usually outnumbers the available resources to address them.
-Similarly, Liblit et al.~\cite{liblit2003bug} remark that several software systems are shipped to known and unknown bugs because of the lack of resources.
+Similarly, Liblit et al.~\cite{liblit2003bug} remark that several software systems are shipped with known ()and unknown) bugs because of the lack of resources.
 
 To alleviate the load on developers working on these issues automated patch generation has been proposed.
-Over the past decade research on this front has gained a lot of traction in the software engineering community.
-Specifically, tools that leverage evolution computation strategies, like GenProg~\cite{leGoues12}, have seen tremendous amounts of success.
+Over the past decade research on this front has gained a lot of traction within the software engineering community.
+Specifically, tools that leverage evolutionary computation strategies, like GenProg~\cite{leGoues12}, have seen tremendous amounts of success.
 
@@
 
-A motivation for this study was our hypothesis that the lack of efficiency of GenProg, in some cases, in this area is not due to the failure of Genetic Algorithms (or any evolutionary computation scheme for that matter), but due to incorrect and perhaps even incomplete modeling of the search space.
+A motivation for this study was our hypothesis that the lack of efficiency of GenProg, in some cases, is not due to the failure of Genetic Algorithms (or any evolutionary computation scheme for that matter), but due to incorrect and perhaps even incomplete modeling of the search space.
 We therefore propose the use of multiobjective search in automated program repair which extends the original single objective GenProg by adding additional objectives to satisfy the fitness function.
-Additionally, to verify if the success of GenProg is indeed due to genetic programming and not mutation/crossover operations, we study to performance of NGSAII~\cite{nsgaii}.
+Additionally, to verify if the success of GenProg is indeed due to genetic programming and not mutation/crossover operations, we study to performance of NSGAII~\cite{nsgaii}.
 It is also worth noting that, to be best of our knowledge, this is the first attempt to study multiobjective patch generation in automated program repair.
@@
 Algorithms like RSRepair, on the other hand, considers either repair effectiveness (as measured by the number patch trials required) or repair efficiency (measured by the number of test case executions).
-It not hard to see that each of these objectives namely, the number of passing test cases, the repair effectiveness, and the repair efficiency, are all important.
+It is not hard to see that each of these objectives namely, the number of passing test cases, the repair effectiveness, and the repair efficiency, are all important.
 Perhaps some are more important than others, but they all play a crucial role nonetheless.
@@
 With this, we seek to validate (or perhaps deprecate) certain claims of studies by Qi et al.~\cite{qi2014}.
-They consider that the success of GenProg is due to the ``mutate'' operation of evolutionary algorithms and not genetic programming.
+They consider that the success of GenProg is due to the mutate operation of evolutionary algorithms and not genetic programming.
 
@@
 We believe this to be untrue and to verify our opinion we replace GP with NSGAII~\cite{nsgaii}.
-NSGAII is a incredibly popular variant of GA (18000+ citations).
-NSGAII consists of a novel sort algorithm that enables it identify better solutions and to converge at these solution much faster.
+NSGAII is an incredibly popular variant of GA (18000+ citations).
+It consists of a novel sort algorithm that enables it identify better solutions and to converge at these solution much faster.
 
@@
 \input{figs/results2.tex}
+\pagebreak
 \section{Experimental Results}
@@
 In addition to this, the usefulness of a promising new algorithm called SWAY\footnote{This algorithm is in current development by our research group}~\cite{chen2016sampling, nair2016accidental} may be also be investigated.
-
+\balance
 \bibliographystyle{unsrt}
